---
title: "Miles per gallon report"
author: "Piya Thavornwong"
date: "12/6/2019"
output: html_document
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
mpg_df <- read_excel("~/Documents/Hult/Dual Degree/Module A/R/Class 9/auto_mpg.xls")

logit_mpg <- glm(mpg_good_bad~cylinders+displacement+horsepower+weight+acceleration+model_year+orogin, data= mpg_df, family = "binomial")
summary(logit_mpg)


```

## Hey senior leader. This is your business insight

The acceleration is not important in considering mpg of the car. Increasing in 1 unit of horsepower, will decrease a chance of being <30 mph car by 6.5%

```{r tree, echo=FALSE}
library(rpart)
library(rpart.plot)

tree_mpg <- rpart(mpg_good_bad~cylinders+displacement+horsepower+weight+acceleration+model_year+orogin, data= mpg_df, method = "class")
rpart.plot(tree_mpg, extra = 1, type = 1)
```

## Insight from Decision Tree

Horsepower and model year are important in analyzing mpg of the car. However, cylinders, displacement, and weight are not important in the decision tree model.